Software Citation Principles

### 2016-02-23 sc-principles/software-citation-principles.tex
small fix to make this build

In astronomy & astrophysics: ASCL \cite{ascl}, AAS journals  AAS/GitHub
workshop \cite{aas-software-index} dedicated to software citation, indexing and discoverability.

>>>>

In astronomy \& astrophysics: ASCL \cite{ascl}, AAS journals  AAS/GitHub
workshop \cite{aas-software-index} dedicated to software citation, indexing and discoverability.
